Constraint Programming - Inside Gecode

### 2014-05-12 paper.tex
corrections of punctuation

	\section{State of the Art}
	\subsection{Variable Domains}
	In constraint programming, a variable is connected to a set of possible values, the so called domain. Depending on the domain, a variable is called an integer, Boolean or floating variable. Possible ranges for a variable $x$ of each domain are:
	\begin{itemize}
		\item Integer: finite or infinite sets like $x \in \mathbb{N}$, $x \in \{-5, 4, 10\}$, \dots
		\item Bool: $x \in \{\text{true}, \text{false}\}$
		\item Float: intervals or unions of intervals like $x \in [-4, 3]$, $x \in [-10, 8] \cup [10, 12]$, \dots
	\end{itemize}
	This distinction is fundamental as especially for floating variables a combinatorial approach to constraint programming is impossible.

@@

	In \emph{Gecode}, it is possible to define custom strategies. However, the user is supported at this point with some standard algorithms which he can use to build custom ones:
	\begin{itemize}
		\item Depth-first search
		\item Limited discrepancy search
		\item Branch-and-bound search
		\item Depth-first search restart optimization
	\end{itemize}

	In the following part, I will discuss the depth-first search, the branch-and-bound search, the limited discrepancy search as candidate for an improved backjumping-strategy, backjumping strategies in general and restart strategies.

	\subsubsection{Depth-First Search}
	The depth-first search was historical the first one which was developed, therefore it is a good point to start explaining search algorithms. The idea behind this search algorithm is that every possible combination of variables is examined. In its basic form, it can not be applied to problems with infinite domains; for problems with such variable domains it is necessary to use for instance branch-and-reduce. Sometimes the depth-first search is also referred to as chronological backtrack search.

@@

	This search is a so-called complete algorithm as it can be proven that all possible solutions will be found \cite[p.~85]{handbookCP}. Because of this characteristic, it is very useful to prove for example that for a certain problem no solution exists. The main drawback is the execution time, as it does an exhaustive search. Maybe even the memory usage can become a problem if during the search many solutions are found.

>>>>

	\section{State of the Art}
	\subsection{Variable Domains}
	In constraint programming a variable is connected to a set of possible values, the so called domain. Depending on the domain, a variable is called an integer, Boolean or floating variable. Possible ranges for a variable $x$ of each domain are:
	\begin{itemize}
		\item Integer: finite or infinite sets like $x \in \mathbb{N}$, $x \in \{-5, 4, 10\}$, \dots
		\item Bool: $x \in \{\text{true}, \text{false}\}$
		\item Float: intervals or unions of intervals like $x \in [-4, 3]$, $x \in [-10, 8] \cup [10, 12]$, \dots
	\end{itemize}
	This distinction is fundamental as especially for floating variables a combinatorial approach to constraint programming is impossible.

@@

	In \emph{Gecode} it is possible to define custom strategies. However, the user is supported at this point with some standard algorithms which he can use to build custom ones:
	\begin{itemize}
		\item Depth-first search
		\item Limited discrepancy search
		\item Branch-and-bound search
		\item Depth-first search restart optimization
	\end{itemize}

	In the following part I will discuss the depth-first search, the branch-and-bound search, the limited discrepancy search as candidate for an improved backjumping-strategy, backjumping strategies in general and restart strategies.

	\subsubsection{Depth-First Search}
	The depth-first search was historical the first one which was developed, therefore it is a good point to start explaining search algorithms. The idea behind this search algorithm is that every possible combination of variables is examined. In its basic form it can not be applied to problems with infinite domains; for problems with such variable domains it is necessary to use for instance branch-and-reduce. Sometimes the depth-first search is also referred to as chronological backtrack search.

@@

	This search is a so-called complete algorithm as it can be proven that all possible solutions will be found \cite[p.~85]{handbookCP}. Because of this characteristic it is very useful to prove for example that for a certain problem no solution exists. The main drawback is the execution time, as it does an exhaustive search. Maybe even the memory usage can become a problem if during the search many solutions are found.
